---
title: "README"
output:
  html_document: default
---

## Practical 2 Bonus Assignment: Lisa Martin

This is my work for Practical 2's Bonus assignment


#### Loading required packages and data:
```{r setup, results = "hide", message=FALSE, warning=FALSE}
#Seperate script used to load required packages
source("code/packageload.R") 

# Loading required data
data <-
  read_rds("data/Fin_Data_SA_US_NKY.rds")

data <- na.omit(data)
```



#### Calculate the cap-weighted monthly index returns for every sector for each country:

I assumed that the formula to use for this is $Index_t = {Market Cap_t}/{Market Cap_{base}}$
In this case, I attempted to calculate a month on month return, therefore the base is the previous month for each period.However, this seemed to cause errors.

Upon consulting my peers, it seemed that I could first calculate the monthly returns and simply weight them by the market cap of each ticker in each sector. 

```{r Question 1, message=FALSE, warning=FALSE}

MonthlyReturns <- 
  #Finding the last observation of each month for each ticker in each sector per country
  data %>% 
  group_by(Universe, BICS_LEVEL_1_SECTOR_NAME, Ticker) %>% 
  mutate(YM = format(date,"%Y_%B")) %>% 
  ungroup() %>% 
  group_by(Universe, BICS_LEVEL_1_SECTOR_NAME, YM) %>%
  filter(date == last(date)) %>% 
  ungroup() %>% 
  
  #Calculating the monthly return for each ticker, Remove the NA returns that would result during JAN
  group_by(Ticker) %>%
  arrange(date) %>% 
  mutate(Returns = TRI/lag(TRI) - 1) %>% 
  mutate(Returns = coalesce(Returns, 0)) %>%  
  ungroup() %>% 
  
  #Create weights for each ticker in terms of their contribution to total market cap
  group_by(Universe, BICS_LEVEL_1_SECTOR_NAME, YM) %>% 
  mutate(SectorMarketCap = sum(Market.Cap)) %>%
  mutate(WeightedMarketCap = Market.Cap/SectorMarketCap) %>% 
  
  #Calculating cap-weighted monthly returns by summing all of the weighted returns per sector
  mutate(WeightedReturns = sum(Returns*WeightedMarketCap)) %>% 
  summarise(IndexReturn = mean(WeightedReturns)) %>%
  
  ungroup()
```




#### Calculate the sharpe ratio for the equally weighted by country, cap-weighted index returns since 2017:

```{rQuestion 2, message=FALSE, warning=FALSE}
MonthlyReturns_Sharpe <- 
  MonthlyReturns  %>% 
  group_by(Universe, BICS_LEVEL_1_SECTOR_NAME) %>% 
  summarise(Sharpe = mean(MonthlyReturns, na.rm = TRUE) / sd(MonthlyReturns, na.rm = TRUE)) %>%
  ungroup() 
```

This (above) method follows the Practical, however returns an error. 

#### Plot all the cumulative returns for the Financials indexes of the three countries (whose Financials index outperformed?):

```{r Question 3, message=FALSE, warning=FALSE}
Fin_Index_Returns <-
  #Finding the last observation of each month for each ticker in each sector per country
  data %>% 
  group_by(Universe, BICS_LEVEL_1_SECTOR_NAME, Ticker) %>% 
  mutate(YM = format(date,"%Y_%B")) %>% 
  ungroup() %>% 
  group_by(Universe, BICS_LEVEL_1_SECTOR_NAME, YM) %>%
  filter(date == last(date)) %>% 
  ungroup() %>% 
  
  #Calculating the monthly return for each ticker, Remove the NA returns that would result during JAN
  group_by(Ticker) %>%
  arrange(date) %>% 
  mutate(Returns = TRI/lag(TRI) - 1) %>% 
  mutate(Returns = coalesce(Returns, 0)) %>%  
  ungroup() %>% 
  
  #Create weights for each ticker in terms of their contribution to total market cap
  group_by(Universe, BICS_LEVEL_1_SECTOR_NAME, YM) %>% 
  mutate(SectorMarketCap = sum(Market.Cap)) %>%
  mutate(WeightedMarketCap = Market.Cap/SectorMarketCap) %>% 
  
  #Calculating cap-weighted monthly returns by summing all of the weighted returns per sector
  mutate(WeightedReturns = sum(Returns*WeightedMarketCap)) %>% 
  ungroup() %>% 
  
  #We need to filter the data to only focus on Financials
  group_by(BICS_LEVEL_1_SECTOR_NAME) %>% 
  filter(BICS_LEVEL_1_SECTOR_NAME %in% "Financials") %>% 
  
  #Next we can calculate cumulative returns per country
  group_by(Universe) %>% 
  mutate(Cum_IndexReturns = cumprod(1 + WeightedReturns)) %>% 
  ungroup()

  #Now we can plot the financial sectors cumulative returns
  ggplot(Fin_Index_Returns) +
  geom_line(aes(x = date, y = Cum_IndexReturns, color=Universe))
  
```

We can see that Japan has underperformed throughout the period in question, but South Africa has outperformed, by reaching the highest cumultive return over the period.  




#### Calculate the JALSH index returns, by filtering the top 95% of Market Cap:
(Tip: use arrange and cumsum of weights. . . careful with your group_bys. . . )

```{r Question 4, message=FALSE, warning=FALSE}
MonthlyReturns_JALSH <- 
  #Finding the last observation of each month for each ticker in each sector per country
  data %>% 
  group_by(Universe, BICS_LEVEL_1_SECTOR_NAME, Ticker) %>% 
  mutate(YM = format(date,"%Y_%B")) %>% 
  ungroup() %>% 
  group_by(Universe, BICS_LEVEL_1_SECTOR_NAME, YM) %>%
  filter(date == last(date)) %>% 
  ungroup() %>% 
  
  #Calculating the monthly return for each ticker, Remove the NA returns that would result during JAN
  group_by(Ticker) %>%
  arrange(date) %>% 
  mutate(Returns = TRI/lag(TRI) - 1) %>% 
  mutate(Returns = coalesce(Returns, 0)) %>%  
  ungroup() %>% 
  
  #Create weights for each ticker in terms of their contribution to total market cap
  group_by(Universe, BICS_LEVEL_1_SECTOR_NAME, YM) %>% 
  mutate(SectorMarketCap = sum(Market.Cap)) %>%
  mutate(WeightedMarketCap = Market.Cap/SectorMarketCap) %>% 
  
  #We only want to do this for JALSH - remove other countries
  filter(Universe %in% "JALSHAll") %>% 
  
  #Arrange the weights and find top 95%
  arrange(WeightedMarketCap) %>% 
  mutate(CumWeight = cumsum(WeightedMarketCap)) %>% 
  filter(CumWeight >= 0.05) %>% 
  
  #Find the weighted returns for the top 95% of JALSH
  mutate(WeightedReturn = sum(Returns*WeightedMarketCap)) %>%
  summarise(JALSHReturn = mean(WeightedReturn)) %>%
  ungroup()

```




#### Calculate and visually compare the rolling 60 day standard deviation for the Materials sectors
of each country:

```{r Question 5, message=FALSE, warning=FALSE}
Mat_IndexReturns <-
  #First we need to filter the data to only focus on Materials
  data %>% 
  group_by(BICS_LEVEL_1_SECTOR_NAME) %>% 
  filter(BICS_LEVEL_1_SECTOR_NAME %in% "Materials") %>% 

  #Calculate the DAILY returns for each stock in the sector per country, Remove the NA returns that would result in the first period
  group_by(Ticker) %>%
  arrange(date) %>% 
  mutate(Returns = TRI/lag(TRI) - 1) %>% 
  mutate(Returns = coalesce(Returns, 0)) %>%  
  ungroup() %>% 
  
  #For each country, calculate the weighted retrun for the sector
  group_by(Universe, date) %>% 
  mutate(SectorMarketCap = sum(Market.Cap)) %>%
  mutate(WeightedMarketCap = Market.Cap/SectorMarketCap) %>% 
  mutate(WeightedReturns = sum(Returns*WeightedMarketCap)) %>% 
  summarise(IndexReturn = mean(WeightedReturns)) %>%
  ungroup() %>% 
  
  
  tbl_xts(., cols_to_xts = "IndexReturn", spread_by = "Universe")

  #Plot the rolling performance of the countries materials sectors using SD
  chart.RollingPerformance(R = Mat_IndexReturns, FUN = "sd", 
      width = 60, main = "Rolling 60 Day Standard Deviation for Materials Sector", 
      legend.loc = "bottom")
```

